%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}
\usepackage{newtxtext}
\usepackage{hyperref}

% Set applicant's personal data for header
\name{Rui Wang}
\contacts{
    (+1) 607-262-1255 
    \quad|\quad 
    \href{mailto:ruiallen@umich.edu}{ruiallen@umich.edu} 
    \quad|\quad 
    \href{https://github.com/Hydraallen}{GitHub} 
    \quad|\quad 
    \href{https://www.linkedin.com/in/rui-wang-546099392/}{LinkedIn} 
}

\makeatletter
\renewcommand\makeheader{
  \begin{center}
    {\printname} 
    \vspace{0.4em} \\
    {\small \@contacts}
  \end{center}
  \vspace*{\afterheaderspace}
}
\makeatother

\begin{document}

	% Print the header
	\makeheader
\begin{cvsection}{Education Profile}
		\begin{cvsubsectionsingleline}{University of Michigan, Ann Arbor \hfill Aug 2025 - Present}
			\begin{itemize}
				\item Master of Science in Information; Concentration in Data Analytics. GPA: 4.000/4.000
			\end{itemize}
		\end{cvsubsectionsingleline}
		\begin{cvsubsectionsingleline}{Shanghai Jiao Tong University - Global College Institute \hfill Sept 2022 - Present}
			\begin{itemize}
				\item Bachelor of Engineering in Electrical and Computer Engineering; Minor in Computer Science. GPA: 3.641/4.000
			\end{itemize}
		\end{cvsubsectionsingleline}
		\begin{cvsubsectionsingleline}{Cornell University \hfill Jan - May 2025}
			\begin{itemize}
				\item Exchange program at College of Engineering. GPA: 3.850/4.000
			\end{itemize}
		\end{cvsubsectionsingleline}
	\end{cvsection}	


\begin{cvsection}{Work \& Leadership Experience}

\begin{cvsubsectionsingleline}{OpenAGI Research Foundation, Inc. \hfill Jan - Dec 2025}
{\small \textit{Software Engineer Intern (Agent Tooling)} \hfill Remote}
\begin{itemize}
    \item Achieved \textbf{state-of-the-art success rate of 83.6} on Online-Mind2Web, significantly outperforming Gemini CUA (69.0), OpenAI Operator (61.3), and Claude Sonnet (61.0).
    \item Engineered Python-based tooling to capture user operations and applied computer-vision methods to reproduce end-to-end workflows for training and evaluation.
    \item Generated operation datasets on OSWorld for terminal and Office tasks, improving data diversity.
    \item Paper: \textit{OSGym: Super-Scalable Distributed Data Engine for Generalizable Computer Agents} (\href{https://arxiv.org/abs/2511.11672}{arXiv:2511.11672}).
\end{itemize}
\end{cvsubsectionsingleline}

\begin{cvsubsectionsingleline}{Salesforce, Inc. \hfill Aug - Dec 2025}
{\small \textit{Data Analyst Intern} \hfill Remote}
\begin{itemize}
    \item Performed \textbf{statistical analysis} on survey data to isolate key factors associated with high-risk AI usage patterns.
    \item Built a \textbf{risk quantification pipeline}, transforming unstructured user feedback into structured risk metrics.
    \item Visualized usage data with \textbf{Tableau}, translating complex data patterns into strategic insights.
\end{itemize}
\end{cvsubsectionsingleline}

\begin{cvsubsectionsingleline}{Shanghai Baosight Software Co., Ltd. \hfill Aug - Sep 2024}
{\small \textit{Machine Learning Intern} \hfill Shanghai, China (On-site)}
\begin{itemize}
    \item Developed short-term metro passenger-flow surge prediction models using \textbf{XGBoost} across \textbf{523 stations}, achieving \textbf{86\% accuracy} to support proactive crowd management.
    \item Engineered complex \textbf{time-series features} and optimized model performance based on \textbf{ROC-AUC}.
\end{itemize}
\end{cvsubsectionsingleline}

\end{cvsection}

\begin{cvsection}{Academic Background}

\begin{cvsubsectionsingleline}{Surgical Video Tool Segmentation \& Evaluation with SAM2 \hfill Jul 2024 -- Jul 2025}
\begin{itemize}
    \item Performed instance segmentation of surgical tools in videos using \textbf{SAM2}. 
    \item Evaluated with \textbf{mIoU} and \textbf{Dice} coefficients across diverse procedures and severe occlusions.
    \item Analyzed failure cases and improved automation by optimizing \textbf{prompt generation}.
	\item Paper accepted by \textit{npj Digital Surgery} (Nature Portfolio): \textit{Systematic Evaluation and Guidelines for Segment Anything Model in Surgical Video Analysis}
. (\href{https://arxiv.org/abs/2501.00525}{arXiv:2501.00525})
\end{itemize}
\end{cvsubsectionsingleline}
\begin{cvsubsectionsingleline}{Online Judge Platform Development \hfill Jan 2024 - Present}
    \begin{itemize}
        \item GitHub: \href{https://github.com/joint-online-judge/JOJ3}{https://github.com/joint-online-judge/JOJ3}
        \item Architected a high-performance Online Judge system using \textbf{Golang}, supporting \textbf{6 programming languages}.
        \item Implemented a \textbf{job queue} model to handle concurrent submissions for execution, scoring, and result feedback.
        \item Designed a secure code execution sandbox using \textbf{Docker API} and \textbf{cgroups} to enforce resource limits.
        \item Deployed \textbf{Prometheus-based} logging and monitoring module for real-time system health tracking.
    \end{itemize}
\end{cvsubsectionsingleline}



	\end{cvsection}

\begin{cvsection}{Skills, Activities \& Interests}
  \begin{cvsubsection}{}{}{}
    \begin{itemize}
       \item \textbf{Languages}: Python, Go, C/C++, SQL, R, Bash/Shell
      \item \textbf{ML \& Data Science}: PyTorch, TensorFlow, Scikit-learn, Pandas, NumPy, OpenCV, Hugging Face
      \item \textbf{Technical Tools}: Linux, Docker, AWS, Git/GitHub Actions, Agile Development, Prometheus, Tableau, \LaTeX
      \item \textbf{Certifications}: Basic SAS Certification; Basic Teaching Assistant Certificate
      \item \textbf{Activities}: Teaching Assistant at SJTU Global College (2023--2025); President of Technical Dept.\ in Student Union (Sept 2022--2025) --- hosted workshops
(\href{https://github.com/Hydraallen/Basic_Git_wksp}{Git},
 \href{https://github.com/Tech-JI/Basic_Git_wksp}{Bash},
 \href{https://github.com/Hydraallen/Latex-vscode}{\LaTeX},
 \href{https://github.com/Hydraallen/Vim_wksp_2023}{Vim},
 \href{https://github.com/Hydraallen/VSCode_wksp}{VSCode})
      \item \textbf{Honors}: 1st Place A2 Data Dive (Nov 2025); Merit Student (Oct 2024); Scholarships (Nov 2024)
    \end{itemize}
  \end{cvsubsection}
\end{cvsection}
	

	
	
\end{document}

