%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}
\usepackage{newtxtext}
\usepackage{hyperref}

% Set applicant's personal data for header
\name{Rui Wang}
% \address{123 Spruce St, Apt 35 \linebreak Philadelphia PA 19103}
\contacts{(+1) 6072621255 \linebreak wangruiallen@gmail.com}

\begin{document}

	% Print the header
	\makeheader
\begin{cvsection}{Education Profile}
		\begin{cvsubsectionsingleline}{University of Michigan, Ann Arbor \hfill Aug 2025 - Present}
			\begin{itemize}
				\item Master of Science in Information, major in Data Analysis, with GPA 4.000/4.000
			\end{itemize}
		\end{cvsubsectionsingleline}
		\begin{cvsubsectionsingleline}{Shanghai Jiao Tong University - Global College Institute \hfill Sept 2022 - Present}
			\begin{itemize}
				\item Major in Electrical and Computer Engineering and Minor in Computer Science, with GPA 3.641/4.000
			\end{itemize}
		\end{cvsubsectionsingleline}
		\begin{cvsubsectionsingleline}{Cornell University \hfill Jan - May 2025}
			\begin{itemize}
				\item Exchange program at College of Engineering, with GPA 3.850/4.000
			\end{itemize}
		\end{cvsubsectionsingleline}
	\end{cvsection}	



\begin{cvsection}{Work \& Leadership Experience}

\begin{cvsubsectionsingleline}{OpenAGI Research Foundation, Inc. \hfill Jan - Aug 2025}
{\small \textit{Software Engineer Intern (Agent Tooling)} \hfill United States (Remote)}
\begin{itemize}
    \item Contributed to \textit{Lux}, achieving state-of-the-art performance on Online-Mind2Web (\textbf{83.6}), outperforming Google Gemini CUA (69.0), OpenAI Operator (61.3), and Anthropic Claude Sonnet 4 (61.0).
    \item Built Python-based tooling to capture user operations and applied computer-vision methods to reproduce end-to-end workflows for training and evaluation.
    \item Generated operation datasets on OSWorld for terminal and Office tasks, improving data diversity.
    \item Paper: \textit{OSGym: Super-Scalable Distributed Data Engine for Generalizable Computer Agents} (\href{https://arxiv.org/abs/2511.11672}{arXiv:2511.11672}).
\end{itemize}
\end{cvsubsectionsingleline}

\begin{cvsubsectionsingleline}{Salesforce, Inc. \hfill Aug - Dec 2025}
{\small \textit{Research Intern} \hfill United States (Remote)}
\begin{itemize}
    \item Completed \textbf{10} user interviews and collected \textbf{200+} survey responses on AI tool usage for privacy analysis.
    \item Visualized usage patterns in Tableau and identified potential privacy risks from data signals and user feedback.
\end{itemize}
\end{cvsubsectionsingleline}

\begin{cvsubsectionsingleline}{Shanghai Baosight Software Co., Ltd. \hfill Aug - Sep 2024}
{\small \textit{Machine Learning Intern} \hfill Shanghai, China (On-site)}
\begin{itemize}
    \item Built short-term metro passenger-flow surge prediction models and achieved \textbf{86\%} accuracy in predicting crowd surges to support operational planning.
    \item Analyzed station-level passenger flow data, engineered time-series features, trained binary classifiers, and iterated with ROC/AUC-driven validation.
\end{itemize}
\end{cvsubsectionsingleline}


\end{cvsection}

	\begin{cvsection}{Academic Background}
		
		
		\begin{cvsubsectionsingleline}{Online judge platform development \hfill Jan 2024 - Present}
		\begin{itemize}
        \item GitHub: \href{https://github.com/joint-online-judge/JOJ3}{https://github.com/joint-online-judge/JOJ3}
        \item Built a Go-based evaluation environment for executing and scoring submissions.
        \item Implemented container-based sandboxing to isolate user code and improve platform reliability.
        \item Developed Prometheus-based logging and monitoring module to track system health in real time.
    	\end{itemize}
		\end{cvsubsectionsingleline}
\begin{cvsubsectionsingleline}{Surgical Video Tool Segmentation \& Evaluation with SAM2 \hfill Jul 2024 -- Oct 2025}
\begin{itemize}
    \item Performed instance segmentation of surgical instruments in videos using SAM2.
    \item Evaluated segmentation performance using mIoU and Dice coefficients, and analyzed model robustness across complex surgical scenarios.
    \item Improved automation and stability by optimizing prompt generation for SAM2 in difficult cases.
	\item Paper: \textit{Systematic Evaluation and Guidelines for Segment Anything Model in Surgical Video Analysis}\\
Accepted by \textit{npj Digital Surgery} (Nature Portfolio), Oct 2025. (\href{https://arxiv.org/abs/2501.00525}{arXiv:2501.00525})
\end{itemize}
\end{cvsubsectionsingleline}

\begin{cvsubsectionsingleline}{Database tool development \hfill Dec 2024}
    \begin{itemize}
        \item Developed basic functionalities for database tool
		\item Added multi-threading, improving efficiency by 3 times.
    \end{itemize}
\end{cvsubsectionsingleline}

\begin{cvsubsectionsingleline}{Service System Modeling and Design \hfill May 2025}
    \begin{itemize}
        \item Modeling and analyzing service systems for ambulance services in NYC.
    \end{itemize}
\end{cvsubsectionsingleline}

	\end{cvsection}


	\begin{cvsection}{Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item \textbf{Programming Languages}: Python, R, C/C++, Go, Matlab, SQL, Elm, SAS, HTML/CSS, JavaScript, Bash
				\item \textbf{Working Space}: Linux, Git, Docker, Latex, Vim, Shell, AWS, Tableau, PowerBI
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}	

	\begin{cvsection}{Campus Activities}
		%!TODO: split project and TA experience
		\begin{cvsubsectionsingleline}{Teaching Assistant in SJTU - Global College}	
			\begin{itemize}
				\item ECE4820J \textit{Operating Systems} Course \hfill Sept - Dec 2025
				\item ECE2810J \textit{Data Structures and Algorithms} Course \hfill Sept - Dec 2024
				\item ENGR1000J \textit{Introduction to Engineering} Course \hfill May - Aug 2024
				\item ENGR1510J \textit{Introduction to Computers and Programming} Course \hfill Sept - Dec 2023
				\item Design projects, hold weekly labs and recitation classes, grade assignments and exams.
				 %TODO: bad word
			\end{itemize}
		\end{cvsubsectionsingleline}
		\begin{cvsubsectionsingleline}{Technical Department of Student Union in SJTU - Global College \hfill Sept 2022 - Present}
			\textit{President and Annual Excellent Volunteer}
			\begin{itemize}
				\item Organize and host multiple workshops , with topics including 
        \href{https://github.com/Hydraallen/Basic_Git_wksp}{Git}, 
        \href{https://github.com/Tech-JI/Basic_Git_wksp}{Bash}, 
        \href{https://github.com/Hydraallen/Latex-vscode}{LaTeX}, 
        \href{https://github.com/Hydraallen/Vim_wksp_2023}{Vim}, 
        \href{https://github.com/Hydraallen/VSCode_wksp}{VSCode}, etc.
				\item Maintain the SJTU - Global College's dance party mini-program.
			\end{itemize}
		\end{cvsubsectionsingleline}
		
		% \begin{cvsubsectionsingleline}{ENGR1000J \textit{Introduction to Engineering} Course \hfill May 2023 - Aug 2023}
		% 	\textit{Team Leader}
		% 	\begin{itemize}
		% 		\item Best Game Design Award. 
		% 		\item Coordinate the team members to promote the project, and be responsible for the design of game mechanics and writing of core code.
		% 	\end{itemize}
		% \end{cvsubsectionsingleline}
		
	


		
	\end{cvsection}
	
	
	\begin{cvsection}{Honors and Scholarships}
		\begin{cvsubsection}{}{}{}
			\begin{itemize}
				\item Nov 2025: \textit{First Place in A2 Data Dive: Campaign Finance Transparency in Michigan.}
				\item May 2025: \textit{Basic SAS(Statistics Analysis System) Certification.}
				\item Nov 2024: \textit{Scholarship for Student Development.}
				\item Oct 2024: \textit{Merit Student of SJTU.}
				\item July 2024: \textit{Third Prize in the China-U.S. Young Maker Competition.}
				\item May 2024: \textit{Software Copyright Registration by the National Copyright Administration of China.}
				\item Dec 2023: \textit{Basic Teaching Assistant Certificate.}
				\item July 2023: \textit{Annual Excellent Volunteer in UM-SJTU JI Student Union.}
				\item June 2023: \textit{Best Game Design Award in ENGR1000J of UM-SJTU JI.}
				\item May 2023: \textit{Honorable Mention in the Mathematical Contest in Modeling organized by COMAP.}
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	
\end{document}

